\documentclass[10pt, oneside]{article}   
\usepackage[margin=1in]{geometry}                		
\geometry{letterpaper}                   		
\usepackage{graphicx}				
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage{multicol}
\include{structure}
\hyphenation{Some-long-word}
\usepackage{longtable}

\begin{document}

\begin{LARGE} \noindent\textbf{Katherine Goode} \end{LARGE} \hfill Curriculum Vitae, October 2021\\
\rule{\textwidth}{1pt}

\vspace{0.25cm}

% CONTACT INFO
\noindent \textsc{Contact Information} \hrulefill
\begin{longtable}{p{3.5cm}p{6.2cm}p{6.2cm}}
& Sandia National Laboratories & \emph{Email:} kjgoode@sandia.gov\\
& P.O. Box 5800 & \emph{Phone}: (505) 844-1998\\
& Albuquerque, NM 87185-0829 & \emph{Website:} https://goodekat.github.io/
\end{longtable}

% EDUCATION
\noindent \textsc{Education} \hrulefill
\begin{longtable}{p{3.5cm}p{13cm}}
\hfill{Jan 2016 - June 2021} & \textbf{Doctor of Philosophy, Statistics}\\
& Iowa State University, Ames, IA\\
& Major Professor: Dr. Heike Hofmann\\
& Dissertation: \emph{Visual Diagnostics for Explaining Machine Learning Models}\\
\\
\hfill{Aug 2013 - May 2015} & \textbf{Master of Science, Statistics}\\
& University of Wisconsin, Madison, WI\\
\\
\hfill{Sep 2009 - June 2013} & \textbf{Bachelor of Arts, Mathematics}\\
& Lawrence University, Appleton, WI\\
& Graduated Magna Cum Laude\\
& Senior Capstone: \emph{An Explanation of Double-Error-Correcting BCH Codes}
\end{longtable}

% AWARDS AND HONORS
\noindent \textsc{Awards and Honors} \hrulefill
\begin{longtable}{p{3.5cm}p{13cm}}
\hfill{2019} & \textbf{Midwest Statistical Machine Learning Colloquium Poster Award}\\
& Awarded for poster ``Using LIME to Interpret a Random Forest Model with an Application to Bullet Matching Data"\\
\\
\hfill{2018} & \textbf{ISU Department of Statistics Dan Mowrey Consulting Excellence Award}\\
& Awarded in recognition of outstanding contributions in the area of statistical consulting while working toward a graduate degree.\\
\\
\hfill{2017} & \textbf{ISU Department of Statistics Award for Experiential Development}\\
& Presented to a graduate student for excellent performance in multiple statistical efforts (teaching and consulting) as part of the graduate program.
\end{longtable}

% RESEARCH INTERESTS
\noindent \textsc{Research Interests} \hrulefill
\begin{longtable}{p{3.5cm}p{13cm}}
& Model Assessment, Interpretation of Machine Learning Algorithms, Data Visualization, Random Forest Models, Mixed Model Residuals, R Package Development
\end{longtable}

% WORK EXPERIENCE
\noindent \textsc{Professional and Research Experience} \hrulefill
\begin{longtable}{p{3.5cm}p{13cm}}
\hfill{Sep 2021 - Current} & \textbf{Postdoctoral Researcher}\\
& \emph{Statistical Sciences Department, Sandia National Laboratories} \vspace{0.1cm}\\
& - Performed research on inverse models with functional data\\
& - Implemented shape analysis methods with national security data\\
& - Prepared manuscript for submission to peer reviewed journal\\
\\
\hfill{Dec 2019 - Sep 2021} & \textbf{Research and Development Intern}\\
& \emph{Statistical Sciences Department, Sandia National Laboratories} \vspace{0.1cm}\\
& - Performed research on neural networks explainability with functional data\\
& - Applied explainability methods to machine learning models\\
& - Presented on work at internal and external events\\
\\
\hfill{Jan 2021 - June 2021} & \textbf{Research Assisstant}\\
& \emph{Department Natural Resource Ecology and Management, Iowa State University}\\
& - Developed R Shiny application to predict taxonomy of fish eggs using random forests\\
& - Assisted in writing manuscript to present the application\\
& - Advised by Dr. Michael Weber and Dr. Philip Dixon\\
\\
\hfill{May 2016 - Dec 2020} & \textbf{Statistical Consultant} (Senior consultant from May 2018 to May 2020)\\
& \emph{Agriculture Experiment Station, Iowa State University} \vspace{0.1cm}\\
& - Helped with administrative decisions and trained new consultants\\
& - \hangindent=0.65em \hangafter=1 Provided statistical support on research projects for graduate students, professors, and staff from the colleges of agriculture and life sciences, engineering, human sciences, liberal arts and sciences, and veterinary medicine\\
& - Assisted with the implementation of analyses in R, SAS, JMP, and SPSS\\
\\
\hfill{May 2019 - Aug 2019} & \textbf{Research Assistant}\\
& \emph{Department Natural Resource Ecology and Management, Iowa State University}\\
& - Assisted with analysis of toxicology study of monarch butterfly larvae exposed to insecticides\\
& - Wrote R code to compute profile confidence intervals for dose response curve models\\
& - Collaboration with Dr. Steven Bradbury and PhD Student Niranjana Krishnan\\
\\
\hfill{Dec 2015} & \textbf{Data Analyst}\\
& \emph{Research Administration Office, Lawrence University} \vspace{0.1cm}\\
& - \hangindent=0.65em \hangafter=1 Analyzed data from a study to compare the academic success and mood towards the university of undergraduates from freshman to sophomore years\\
& - \hangindent=0.65em \hangafter=1 Performed statistical analyses using SPSS\\
\\
& \textbf{Data Collection Assistant}\\
\hfill{Sep 2014 - May 2015} & \emph{Research Administration Office, Lawrence University} \vspace{0.1cm}\\
& - \hangindent=0.65em \hangafter=1 Assisted with the data collection for a study on the evaluation of warning lights installed at a busy crosswalk on the university campus\\
& - \hangindent=0.65em \hangafter=1 Used Tracker software to determine the deceleration rate of vehicles from videos taken of cars approaching the crosswalk
\end{longtable}

% PAPERS AND TECHNICAL REPORTS
\noindent \textsc{Papers and Technical Reports} \hrulefill

\begin{longtable}{p{16.5cm}}
\hangindent=1.5em \textbf{Goode K.}, M. J. Weber, A. Matthews, and C. L. Pierce. In press. Evaluation of a random forest model to identify invasive carp eggs based on morphometric features. North American Journal of Fisheries Management. https://doi.org/10.1002/nafm.10616.\\
\\
\hangindent=1.5em \textbf{Goode K.} and H. Hofmann. 2021. Visual diagnostics of an explainer model: Tools for the assessment of LIME explanations. Stat Anal Data Min: The ASA Data Sci Journal: 1-16. https://doi.org/10.1002/sam.11500.\\
\\
\hangindent=1.5em Dixon, P. M., \textbf{K. Goode}, and C. Lay. 2020. Profile likelihood confidence intervals for ECx. Iowa State Digital Repository: Technical Reports. https://lib.dr.iastate.edu/stat\_las\_reports/1.\\
\\
\hangindent=1.5em Ball, E. E., \textbf{K. Goode}, and M. J. Weber. 2019. Effects of transport duration and water quality on age-0 walleye stress and survival. North American Journal of Aquaculture 82:33–42. https://doi.org/10.1002/naaq.10114.\\
\\
\emph{Under Review/In Preparation}\\
\\
\hangindent=1.5em English, L., J. Niemi, B. Wilsey, \textbf{K. Goode}, and M. Liebman. Understanding the variation in vegetation composition of prairie restorations within crop yields. \emph{Submitted to Ecological Restoration}.\\
\\
\hangindent=1.5em \textbf{Goode, K.}, M. J. Weber, and P. M. Dixon. WhoseEgg: Classification software for invasive carp eggs. \emph{Submitted to Fisheries Magazine}.\\
\\
\hangindent=1.5em Lansing, J., L. D. Ellingson, \textbf{K. Goode}, and J. D. Meyer. Comparison of self-efficacy for reducing sedentary time to self-efficacy for increasing physical activity. \emph{Submitted to Psychology of Sport and Exercise}.\\
\\
\hangindent=1.5em \textbf{Goode, K.}, D. Ries, H. Hofmann, and J. D. Tucker. An explainable pipeline for machine learning with functional data.\\
\\
\hangindent=1.5em \textbf{Goode, K.} and H. Hofmann. Tracing trees: Extending trace plots to visualize random forest tree variability.
\end{longtable}

% TALKS
\noindent \textsc{Contributed Talks} \hrulefill
\begin{longtable}{p{16.5cm}}
\hangindent=1.5em \textbf{Goode, K.}, Ries, D., and Zollweg, J. ``Explaining Neural Networks with Functional Data Using PCA and Feature Importance". AAAI 2020 Fall Symposium on AI in the Government and Public Sector. November 13-14, 2020.\\
\\
\hangindent=1.5em \textbf{Goode, K.} and Hofmann, H. ``Visual Diagnostics of a Model Explainer: Tools for the Assessment of LIME Explanations from Random Forests". Joint Statistical Meetings. July 29, 2019.\\
\\
\hangindent=1.5em \textbf{Goode, K.} ``A Review and Discussion of Residuals for Mixed Models". NCCC-170 Meeting. June 20, 2019.
\end{longtable}

% POSTERS
\noindent \textsc{Contributed Posters} \hrulefill
\begin{longtable}{p{16.5cm}}
\hangindent=1.5em \textbf{Goode, K.} and Hofmann, H. ``Using LIME to Interpret a Random Forest Model with an Application to Bullet Matching Data", Midwest Statistical Machine Learning Colloquium. May 13, 2019.\\
\\ 
\hangindent=1.5em \textbf{Goode, K.} and Hofmann, H. ``Using LIME to Interpret a Random Forest Model with an Application to Bullet Matching Data", Iowa State University Graduate and Professional Student Research Conference. April 10, 2019.\\
\\ 
\hangindent=1.5em \textbf{Goode, K.} and Rey, K. ``Introducing ggResidpanel: An R Package for Easy Visualization of Residuals". Kansas State University Conference on Applied Statistics in Agriculture. Contributed Poster. May 2018.
\end{longtable}

% SOFTWARE
\noindent \textsc{Software Development} \hrulefill

\begin{longtable}{p{16.5cm}}
\hangindent=1.5em \textbf{\texttt{WhoseEgg}: An R Shiny app for predicting the identification of fish eggs with an objective of detecting invasive carp.} Joint work with Dr. Michael Weber and Dr. Philip Dixon. Available at \texttt{https://whoseegg.stat.iastate.edu/}. Source code available at \texttt{https://github.com/goodekat/WhoseEgg}.\\
\\
\hangindent=1.5em \textbf{\texttt{ggResidpanel}: An R package for easy visualization of model diagnostic plots.} Joint work with Dr. Kathleen Rey. Source code available at \texttt{https://goodekat.github.io/ggResidpanel/}.\\
\\
\hangindent=1.5em \textbf{\texttt{limeaid}: An R package for visually diagnosing LIME explanations.} Source code available at \texttt{https://github.com/goodekat/limeaid}.\\
\\
\hangindent=1.5em \textbf{\texttt{redres}: An R for computing residuals for linear mixed effects models.} Joint work with Kellie McClernon, Jing Zhao, Yudi Zhang, and Yonghui Huo. Source code available at \texttt{https://github.com/goodekat/redres}.
\end{longtable}

% WORKSHOPS
\noindent \textsc{Workshops} \hrulefill

\begin{longtable}{p{3.5cm}p{13cm}}
\hfill{July 2019} & \textbf{Industrial Math/Stat Modeling (IMSM) Workshop for Graduate Students}\\
& \emph{The Statistical and Applied Mathematical Sciences Institute (SAMSI)} \vspace{0.1cm}\\
& - \hangindent=0.65em \hangafter=1 Two week research workshop\\
& - \hangindent=0.65em \hangafter=1 Worked in a research group mentored by senior statisticians from Rho Inc.\\
& - \hangindent=0.65em \hangafter=1 Analyzed continuously monitored glucose data using functional data analysis\\
& - \hangindent=0.65em \hangafter=1 Assisted with the writing of a report and presentation on the research analysis\\
\end{longtable}

% TEACHING
\noindent \textsc{Teaching Experience} \hrulefill
\begin{longtable}{p{1.4cm}p{2.1cm}p{13cm}}
\textbf{Seminar} & \hfill{Aug 2018} & \textbf{Predictive plant phenomics graduate student statistics bootcamp}\\
\textbf{Leader} & \hfill{and 2019} & \emph{Iowa State University}\\
& & - Led a one day statistics bootcamp\\
& & - Discussed randomization, confidence intervals, and design of experiments\\
& & - Prepared slides\\
\\
\textbf{Instructor} & \hfill{Spring 2016} & \textbf{STAT 101: Introduction to statistics}\\
& & \emph{Iowa State University}\\
& & - Prepared and led lectures\\
& & - Wrote and graded exams\\
& & \hangindent=0.65em \hangafter=1 - Topics included summary statistics, visualization, normal distribution, hypothesis testing, confidence intervals, and JMP\\
\\
& \hfill{Fall 2015} & \textbf{MATH 107: Elementary statistics}\\
& & \emph{Lawrence University}\\
& & - Organized the curriculum\\
& & - Prepared and graded homework and exams\\
& & \hangindent=0.65em \hangafter=1 - Topics included summary statistics, visualizations, randomization tests, bootstrap, normal distribution, hypothesis testing, confidence intervals, and R\\
\\
\textbf{Teaching} & \hfill{Spring 2015} & \textbf{BMI 552: Regression methods for population health graduate students}\\
\textbf{Assistant} & & \emph{UW Madison}\\
& & - Taught labs\\
& & - Held office hours\\
& & \hangindent=0.65em \hangafter=1 - Topics included simple and multiple linear regression, logistic regression, survival analysis, and SAS\\
\\
& \hfill{Fall 2014} & \textbf{BMI 551: Introduction to biostatistics for population health graduate students}\\
& & \emph{UW Madison}\\
& & - Taught labs\\
& & - Held office hours\\
& & - \hangindent=0.65em \hangafter=1 Topics included summary statistics, visualizations, probability, normal distributions, hypothesis testing, confidence intervals, and R.\\
\\
& \hfill{Summer 2014} & \textbf{STAT 301: Introduction to statistical methods for non-statistics majors}\\
& & \emph{UW Madison}\\
& & - Prepared and led discussions\\
& & - Graded homework and exams\\
& & - Held office hours\\
& & - \hangindent=0.65em \hangafter=1 Topics included summary statistics, visualizations, probability, normal distributions, hypothesis testing, and confidence intervals\\
\\
& \hfill{Spring 2014} & \textbf{STAT 302: Accelerated introduction to statistical methods for statistics undergraduate majors}\\
& & \emph{UW Madison}\\
& & - Prepared and led discussions\\
& & - Graded homework and exams\\
& & - Held office hours\\
& & - \hangindent=0.65em \hangafter=1 Topics included summary statistics, visualizations, randomization tests, bootstrap, normal distribution, hypothesis testing, confidence intervals, and R\\
\\
& \hfill{Fall 2013} & \textbf{STAT 371: Introductory applied statistics for the life sciences}\\
& & \emph{UW Madison}\\
& & - Prepared and led discussions\\
& & - Graded homework and exams\\
& & - Held office hours and worked in the statistics help room\\
& & - \hangindent=0.65em \hangafter=1 Topics included summary statistics, visualizations, probability, normal distributions, hypothesis testing, confidence intervals, and R\\
\\
\textbf{Mentor} & \hfill{Sep 2014 - } & \textbf{Academic Mentor for Minority and First Generation Undergraduates}\\
& \hfill{May 2015} & \emph{Center for Academic Excellence, University of Wisconsin, Madison} \vspace{0.1cm}\\
& & - \hangindent=0.65em \hangafter=1 Mentored minority and first generation undergraduate students enrolled in statistics courses\\
& & - \hangindent=0.65em \hangafter=1 Met weekly throughout the semester with individuals or small groups to review statistical concepts from class and make the material approachable\\
& & - \hangindent=0.65em \hangafter=1 Discussed and encouraged strategies for academic success\\
\\
\textbf{Tutor} & \hfill{Fall 2014 -} & Tutored undergraduate students in various introductory statistics courses at UW \\
& \hfill{Spring 2015} & Madison
\end{longtable}

% SERVICE
\noindent \textsc{Service} \hrulefill
\begin{longtable}{p{3.5cm}p{13cm}}
\hfill{Sep 2019 - May 2020} & Iowa State statistical graphics working group weekly meeting organizer\\
\hfill{Sep 2018 - May 2019} & Graduate student representative to ISU statistics department faculty meetings\\
\hfill{Sep 2017 - May 2019} & Recycling coordinator for ISU STATers (Statistics Graduate Student Organization)\\
\hfill{Sep 2017 - May 2019} & Treasurer and member of StatCom (Statistics in the Community) at Iowa State
\end{longtable}

% COMPUTING
\noindent \textsc{Computing Skills} \hrulefill
\begin{longtable}{p{16.5cm}}
Working Knowledge: GitHub, JMP, \LaTeX, Python, R, R Markdown, SAS, Shiny\\
Basic Knowledge: C, SPSS
\end{longtable}

\end{document}

